Spatiotemporal Optimization of Cosmological Particel-Mesh Simulation

### 2022-11-25 docs/papers/sto/sto.tex
sto paper: add cubic Hermite equations

\usepackage{microtype}
\usepackage{newpxtext, eulerpx}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{graphicx}
%\usepackage{booktabs}

@@

>>>>

\usepackage{microtype}
\usepackage{newpxtext, eulerpx}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{booktabs}

@@

Given two snapshots at $a_i$ and $a_{i+1}$, we get the particle displacements
in between at $a$ using interpolation with the cubic Hermite spline,
\begin{align}
  \bm{x}(a) =\ &h_{00}(\alpha)\bm{x}_i + h_{10}(\alpha)(a_{i+1} - a_i)\bm{v}_i + \nonumber\\
           &h_{01}(\alpha)\bm{x}_{i+1} + h_{11}(\alpha)(a_{i+1} - a_i)\bm{v}_{i+1} \,,
\end{align}
where $\alpha := (a - a_i)/(a_{i+1} - a_i)$ and the Hermite basis functions read
\begin{align}
  h_{00}(\alpha) &= 2\alpha^3 - 3\alpha^2 + 1 \,,\nonumber\\
  h_{10}(\alpha) &= \alpha^3 - 2\alpha^2 + \alpha \,,\nonumber\\
  h_{01}(\alpha) &= -2\alpha^3 + 3\alpha^2 \,,\nonumber\\
  h_{11}(\alpha) &= \alpha^3 - \alpha^2 \,.
\end{align}
The particle velocity is then given by the derivative $d\bm{x}/da$.
